A 3d curvilinear skeletonization algorithm with application to path tracing

### 2012-09-14 application_to_path_tracing.tex
Modifying image

\section{Conclusion}

We presented in this article a new skeletonization algorithm that both preserves geometrical features of objects and produces a pure curvilinear skeleton. These two properties allow us to improve the path tracing algorithm in guiding the rays towards the main illuminated area of the scene. Our algorithm is faster and produce less noise than the classical path tracing method.

>>>>

\section{Conclusion}
We presented in this article a new skeletonization algorithm that both preserves geometrical features of objects and produces a pure curvilinear skeleton. These two properties allow us to improve the path tracing algorithm in guiding the rays towards the main illuminated area of the scene. Our algorithm is faster and produce less noise than the classical path tracing method.
